---
title: "TNUM"
author: "Wang Jingyao Zhang Hao Wang Shengbo Jin Yan"
date: '2022-11-09'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

### Assignment Part 1: Text Analysis with Truenumbers

#Report
 The Time Machine that written by H.G. Wells is a fiction that about the main character's experience of time traveling. It tells the story of a time traveler who uses a time machine to go to the Victorian England in the year 802,701. In this report, we will use the tnum in R to get a deeper understanding of the character, Weena.
 
Weena is one of the Eloi. Although the Time Traveller reports that it is difficult to distinguish gender among the Eloi, he seems quite sure that Weena is female. He easily saves her from being washed down the river, and she eagerly becomes his friend. Her behavior toward him is not unlike that of a pet or small child.

Below, we use tnum to locate some key words including: Weena, Eloi, and friend. 


```{r}
#access
devtools::install_github("arazdow/tnum/tnum")
library(tnum) 
tnum.loadLibs() 
tnum.authorize(ip = 'mssp.truenum.com:8080', creds = 'wjingyao@bu.edu:salmon')
```
```{r}
#Weena
Weena_ch1<-tnum.query("subj:Time_Machine:Chapter:1:* and stringval:Weena")
Weena_ch2<-tnum.query("subj:Time_Machine:Chapter:2:* and stringval:Weena")
Weena_ch3<-tnum.query("subj:Time_Machine:Chapter:3:* and stringval:Weena")
Weena_ch4<-tnum.query("subj:Time_Machine:Chapter:4:* and stringval:Weena")
Weena_ch5<-tnum.query("subj:Time_Machine:Chapter:5:* and stringval:Weena")
Weena_ch6<-tnum.query("subj:Time_Machine:Chapter:6:* and stringval:Weena")
Weena_ch7<-tnum.query("subj:Time_Machine:Chapter:7:* and stringval:Weena")
Weena_ch8<-tnum.query("subj:Time_Machine:Chapter:8:* and stringval:Weena")
Weena_ch9<-tnum.query("subj:Time_Machine:Chapter:9:* and stringval:Weena")
Weena_ch10<-tnum.query("subj:Time_Machine:Chapter:10:* and stringval:Weena")
Weena_ch11<-tnum.query("subj:Time_Machine:Chapter:11:* and stringval:Weena")
Weena_ch12<-tnum.query("subj:Time_Machine:Chapter:12:* and stringval:Weena")
Weena_ch13<-tnum.query("subj:Time_Machine:Chapter:13:* and stringval:Weena")
Weena_ch14<-tnum.query("subj:Time_Machine:Chapter:14:* and stringval:Weena")
Weena_ch15<-tnum.query("subj:Time_Machine:Chapter:15:* and stringval:Weena")
Weena_ch16<-tnum.query("subj:Time_Machine:Chapter:16:* and stringval:Weena")
```

```{r}

frequency_Weena<-c(0,0,0,0,0,0,0,7,7,12,9,16,1,0,0,1)
Chapter_Weena<-c()
for(i in 1:16){
  nam<-paste("Weena_ch",i,sep="")
  Chapter_Weena<-append(Chapter_Weena,nam)
}
result_Weena<-as.data.frame(cbind(frequency_Weena,Chapter_Weena))

#tag
tag_Weena<-mapply(FUN=tnum.addTag,
                    guid=Weena_ch12$id,
                    tag="Weena Most",
                    text="Weena shows up the most in this chapter")

```


```{r}
#Eloi

Eloi_ch7<-tnum.query("subj:Time_Machine:Chapter:7:* and stringval:Eloi")
Eloi_ch8<-tnum.query("subj:Time_Machine:Chapter:8:* and stringval:Eloi")
Eloi_ch9<-tnum.query("subj:Time_Machine:Chapter:9:* and stringval:Eloi")
Eloi_ch10<-tnum.query("subj:Time_Machine:Chapter:10:* and stringval:Eloi")
Eloi_ch11<-tnum.query("subj:Time_Machine:Chapter:11:* and stringval:Eloi")
Eloi_ch12<-tnum.query("subj:Time_Machine:Chapter:12:* and stringval:Eloi")

```
```{r}
frequency_Eloi<-c(0,2,2,4,0,0)
Chapter_Eloi<-c()
for(i in 7:12){
  nam<-paste("Eloi_ch",i,sep="")
  Chapter_Eloi<-append(Chapter_Eloi,nam)
}
result_Eloi<-as.data.frame(cbind(frequency_Eloi,Chapter_Eloi))
result_Eloi<-result_Eloi%>%arrange(desc(result_Eloi$frequency_Eloi))

#tag
tag_Eloi<-mapply(FUN=tnum.addTag,
                    guid=Eloi_ch10$id,
                    tag="Eloi Most",
                    text="Eloi shows up the most in this chapter")
```



```{r}
#friend
friend_ch7<-tnum.query("subj:Time_Machine:Chapter:7:* and stringval:friend")
friend_ch8<-tnum.query("subj:Time_Machine:Chapter:8:* and stringval:friend")
friend_ch9<-tnum.query("subj:Time_Machine:Chapter:9:* and stringval:friend")
friend_ch10<-tnum.query("subj:Time_Machine:Chapter:10:* and stringval:friend")
friend_ch11<-tnum.query("subj:Time_Machine:Chapter:11:* and stringval:friend")
friend_ch12<-tnum.query("subj:Time_Machine:Chapter:12:* and stringval:friend")
```
```{r}
frequency_friend<-c(0,4,0,2,0,1)
Chapter_friend<-c()
for(i in 7:12){
  nam<-paste("friend_ch",i,sep="")
  Chapter_friend<-append(Chapter_friend,nam)
}
result_friend<-as.data.frame(cbind(frequency_friend,Chapter_friend))
result_friend<-result_friend%>%arrange(desc(result_friend$frequency_friend))

#tag
tag_friend<-mapply(FUN=tnum.addTag,
                    guid=friend_ch8$id,
                    tag="friend Most",
                    text="friend shows up the most in this chapter")
```

#Conlusion
Consider Weena as an example, We first find the number of occurrences of the word "Weena" in each chapter by using tnum.query(). Then we sort the number of its appearances, and we can find that Weena appears the most times in Chapter 12, a total of sixteen times and it appears 12 times in Chapter 10. We did the same step with the other three words, and we can notice that the 4 keywords we chose appeared the most at the same time in Chapter 8.

Then, we find a summary about Chapter 8~12, which is exactly essence about charater Weena in this book.
  "When Weena and the Time Traveler visit the Palace of Green Porcelain, they discover that it is indeed constructed of green porcelain, just as it seems. They discover that it is a destroyed museum as well. The Time Traveler recovers some camphor, a flammable chemical sometimes found in torches, from a chemistry display. He had ran out of matches, so he is delighted to find some preserved ones. He is also amazed by the utterly rotted remnants of books that he discovers in one of the hallways. He observes Weena becoming worried as he investigates a vast hall filled with machines. He notices the sound of Morlocks as he turns to face the hallway's dark end. He destroys a lever from one of the machines and runs away. He plans to leave the museum quickly and get back to the future."


### Assignment Part 2: Analysis of Numeric Data with Truenumbers

```{r}

#wealthy
wealthy<-tnum.query("prop:median_household_income* and numval:>90000")
result_wealthy<-wealthy%>%arrange(desc(si_value))
result_wealthy_most<-result_wealthy[1,]
tag_wealthy<-mapply(FUN=tnum.addTag,
                    guid=result_wealthy_most$id,
                    tag="The most wealthy county",
                    text="the most wealthy county in New England Counties")
tnum.getTagsOfTn(result_wealthy_most[1,]$id)
kable(result_wealthy)

tnum.postStatement(
  stmt="The most wealthy county in New England is 107717",
  notes="The first truenumber"
)


```

First, We want to find the most wealthy county in New England, we choose the median household income as the factor, using the query function to search all the county, next arrange the value of factor and then the first county is the most wealthy county which is 107717.

```{r}
tnum.graphPathList(result_wealthy$subject)
```

The graph means the construct of wealthy county in New England, from the Country to State and then County, the last construct is town, it is clear to see the relationship between them.

```{r}
tnum.graphTnumList(result_wealthy,tagpattern = ".*")
```

the graph is the extension of last graph, every countis were tagged by label, we separate them as three levels, from wealthy to poor and at risk, it is easy to handle the situation of every counties.for the rest of below, we using 9 of other properties to explore the relationship by the same method of coding but not graphing.

```{r}
#at risk
# risk<-tnum.query("prop:population:no_health_insurance:*")
# result_risk<-risk%>%arrange(desc(si_value))
# result_risk_most<-result_risk[1,]
# tag_risk<-mapply(FUN=tnum.addTag,
#                     guid=result_risk_most$id,
#                     tag="The most at risk county",
#                     text="the most at risk county in New England Counties")
# tnum.getTagsOfTn(result_risk_most[1,]$id)
# kable(result_risk_most)
# 
# tnum.postStatement(
#   stmt="The value of the most at risk county in New England is 44789",
#   notes="The Second truenumber"
# )
```

```{r}
#large
# education<-tnum.query("prop:population:bachelors")
# result_education<-education%>%arrange(desc(si_value))
# result_education_large<-result_education[1,]
# tag_risk<-mapply(FUN=tnum.addTag,
#                     guid=result_education_large$id,
#                     tag="The large education county",
#                     text="the largest education population county in New England Counties")
# tnum.getTagsOfTn(result_education_large[1,]$id)
# kable(result_education_large)
# 
# tnum.postStatement(
#   stmt="The value of the largest education population in New England is 308958",
#   notes="The Third truenumber"
# )
```


```{r}
#master population
# master<-tnum.query("prop:population:masters")
# result_master<-master%>%arrange(desc(si_value))
# result_master_most<-result_master[1,]
# tag_risk<-mapply(FUN=tnum.addTag,
#                     guid=result_master_most$id,
#                     tag="The most masters population county",
#                     text="the most masters population county in New England Counties")
# tnum.getTagsOfTn(result_master_most[1,]$id)
# kable(result_master_most)
# 
# tnum.postStatement(
#   stmt="The value of the most masters population in New England is 218821",
#   notes="The Fourth truenumber"
# )
```

```{r}
#professional population
# pro_popul<-tnum.query("prop:population:professional* ")
# result_pro_popul<-pro_popul%>%arrange(desc(si_value))
# result_pro_popul_most<-result_pro_popul[1,]
# tag_pro_popul<-mapply(FUN=tnum.addTag,
#                     guid=result_pro_popul_most$id,
#                     tag="The most professional population county",
#                     text="the most professional population county in New England Counties")
# tnum.getTagsOfTn(result_pro_popul_most[1,]$id)
# kable(result_pro_popul_most)
# 
# tnum.postStatement(
#   stmt="The most professional population county in New England is 46031",
#   notes="The fifth truenumber"
# )
```

```{r}
#doctorate
# doctorate<-tnum.query("prop:population:doctorate* ")
# result_doctorate<-doctorate%>%arrange(desc(si_value))
# result_doctorate_most<-result_doctorate[1,]
# tag_doctorate<-mapply(FUN=tnum.addTag,
#                     guid=result_doctorate_most$id,
#                     tag="The most doctorate population county",
#                     text="the most doctorate population county in New England Counties")
# tnum.getTagsOfTn(result_doctorate_most[1,]$id)
# kable(result_doctorate_most)
# tnum.postStatement(
#   stmt="The most doctorate population county in New England is 58422",
#   notes="The sixth truenumber"
# )
```

```{r}
#Households
# households<-tnum.query("prop:households* ")
# result_households<-households%>%arrange(desc(si_value))
# result_households_most<-result_households[1,]
# tag_households<-mapply(FUN=tnum.addTag,
#                     guid=result_households_most$id,
#                     tag="The most households county",
#                     text="the most households county in New England Counties")
# tnum.getTagsOfTn(result_households_most[1,]$id)
# kable(result_households_most)
# 
# tnum.postStatement(
#   stmt="The most households county in New England is 604384",
#   notes="The seventh truenumber"
# )
```

```{r}
#population:associates
# associates<-tnum.query("prop:population:associates* ")
# result_associates<-associates%>%arrange(desc(si_value))
# result_associates_most<-result_associates[1,]
# tag_associates<-mapply(FUN=tnum.addTag,
#                     guid=result_associates_most$id,
#                     tag="The most associates population county",
#                     text="the most associates population county in New England Counties")
# tnum.getTagsOfTn(result_associates_most[1,]$id)
# kable(result_associates_most)
# 
# tnum.postStatement(
#   stmt="The most associates population county in New England is 64774",
#   notes="The eighth truenumber"
# )
```

```{r}
#rate:graduation
# graduation<-tnum.query("prop:rate:graduation* ")
# result_graduation<-graduation%>%arrange(desc(si_value))
# result_graduation_most<-result_graduation[1,]
# tag_graduation<-mapply(FUN=tnum.addTag,
#                     guid=result_graduation_most$id,
#                     tag="The most graduation rate county",
#                     text="the most graduation rate county in New England Counties")
# tnum.getTagsOfTn(result_graduation_most[1,]$id)
# kable(result_graduation_most)
# 
# tnum.postStatement(
#   stmt="The most graduation rate county in New England is 58%",
#   notes="The ninth truenumber"
# )
```

```{r}
#rate:flow:average
# flowrate<-tnum.query("prop:rate:flow:average* ")
# result_flowrate<-flowrate%>%arrange(desc(si_value))
# result_flowrate_most<-result_flowrate[1,]
# tag_flowrate<-mapply(FUN=tnum.addTag,
#                     guid=result_flowrate_most$id,
#                     tag="The most flow rate county",
#                     text="the most flow rate county in New England Counties")
# tnum.getTagsOfTn(result_flowrate_most[1,]$id)
# kable(result_flowrate_most)
# 
# tnum.postStatement(
#   stmt="The most flow rate county in New England is 21.4",
#   notes="The tenth truenumber"
# )
```








